Is it time for an NBA expansion?

### 2024-04-16 paper/paper.qmd
Updated Model

# Simulating data
set.seed(123)  # For reproducibility
sim_nba_data <- data.frame(
  Year = rep(1980:2023, times = 10),  # Simulate 10 records per year
  Num_teams = c(rep(22, each = 1 * 10),
                rep(23, each = 8 * 10),
                rep(25, each = 1 * 10),
                rep(27, each = 6 * 10),
                rep(29, each = 9 * 10),
                rep(30, each = 19 * 10)),  # Adjusted each parameter as needed
  PTS = rnorm(440, mean = mean(full_nba_data$PTS), sd = sd(full_nba_data$PTS)),  
  AST = rnorm(440, mean = mean(full_nba_data$AST), sd = sd(full_nba_data$AST)), 
  TRB = rnorm(440, mean = mean(full_nba_data$TRB), sd = sd(full_nba_data$TRB)),  
  STL = rnorm(440, mean = mean(full_nba_data$STL), sd = sd(full_nba_data$STL)),  
  BLK = rnorm(440, mean = mean(full_nba_data$BLK), sd = sd(full_nba_data$BLK)),  
  TOV = rnorm(440, mean = mean(full_nba_data$TOV), sd = sd(full_nba_data$TOV)) 
)

# Fit a multiple linear regression model
nba_model <- lm(PTS ~ Year * Num_teams^2 + AST^2 + TRB^2 + STL + BLK + TOV, data = sim_nba_data)
model_ny <- lm(PTS ~ Num_teams + AST + TRB + STL + BLK + TOV, data = sim_nba_data)

>>>>

# Simulating data
set.seed(123)  # For reproducibility
sim_nba_data <- data.frame(
  Year = rep(1980:2023, times = 10),  # Simulate 10 records per year
  Num_Teams = c(rep(22, each = 1 * 10),
                rep(23, each = 8 * 10),
                rep(25, each = 1 * 10),
                rep(27, each = 6 * 10),
                rep(29, each = 9 * 10),
                rep(30, each = 19 * 10)),  # Adjusted each parameter as needed
  PTS = rnorm(440, mean = mean(full_nba_data$PTS), sd = sd(full_nba_data$PTS)),  
  AST = rnorm(440, mean = mean(full_nba_data$AST), sd = sd(full_nba_data$AST)), 
  TRB = rnorm(440, mean = mean(full_nba_data$TRB), sd = sd(full_nba_data$TRB)),  
  STL = rnorm(440, mean = mean(full_nba_data$STL), sd = sd(full_nba_data$STL)),  
  BLK = rnorm(440, mean = mean(full_nba_data$BLK), sd = sd(full_nba_data$BLK)),  
  TOV = rnorm(440, mean = mean(full_nba_data$TOV), sd = sd(full_nba_data$TOV)) 
)

# Fit a multiple linear regression model
nba_model <- lm(PTS ~ Year * Num_Teams^2 + AST^2 + TRB^2 + STL + BLK + TOV, data = sim_nba_data)
model_ny <- lm(PTS ~ Num_Teams + AST + TRB + STL + BLK + TOV, data = nba_data)
